%-------------------------
% Resume in Latex
% Author : Abey George
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\RequirePackage{tikz}
\RequirePackage{xcolor}
\RequirePackage{fontawesome}
\usepackage{tikz}
\usetikzlibrary{svg.path}


\definecolor{cvblue}{HTML}{0E5484}
\definecolor{black}{HTML}{130810}
\definecolor{darkcolor}{HTML}{0F4539}
\definecolor{cvgreen}{HTML}{3BD80D}
\definecolor{taggreen}{HTML}{00E278}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{name}{black}
\colorlet{tagline}{darkcolor}
\colorlet{heading}{darkcolor}
\colorlet{headingrule}{cvblue}
\colorlet{accent}{darkcolor}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}



%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


% \pagestyle{fancy}
% \fancyhf{}  % clear all header and footer fields
% \fancyfoot{}
% \renewcommand{\headrulewidth}{0pt}
% \renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large#1} & \textbf{\small #2} \\
      \textit{\large#3} & \textit{\small #4} \\
      
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\newcommand\sbullet[1][.5]{\mathbin{\vcenter{\hbox{\scalebox{#1}{$\bullet$}}}}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------


\begin{center}
    {\Huge \scshape Nam Anh Pham Hoang (Harris)} \\ \vspace{1pt}
    Ho Chi Minh City, Vietnam \\ \vspace{1pt}
    \small \href{tel:+84 869 481 840}{ \raisebox{-0.1\height}\faPhone\ \underline{+84 869 481 840} ~}
    \href{mailto:phnanh.harris@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{phnanh.harris@gmail.com}} ~ 
    \href{https://linkedin.com/in/phna-harris}{\raisebox{-0.2\height}\faLinkedinSquare\ \underline{phna-harris}}  ~
    \href{https://github.com/phnaharris}{\raisebox{-0.2\height}\faGithub\ \underline{phnaharris}} ~
    \href{https://www.hackerrank.com/phnaharris}{\raisebox{-0.2\height}\faHackerrank\ \underline{phnaharris}} \\
    \href{https://phnaharris.github.io/}{\raisebox{-0.2\height}\faGlobe\  \underline{https://phnaharris.github.io/}} ~
    \href{https://phnaphnt.github.io/}{\raisebox{-0.2\height}\faGlobe\  \underline{https://phnaphnt.github.io/}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {VNUHCM - University of Science}{08 2018 -- 08 2023}
      %{Bachelor's degree - \textbf{CGPA} - \textbf{6.8}}{Ho Chi Minh City, Vietnam}
      {Bachelor's degree (Computer Science major)}{Ho Chi Minh City, Vietnam}
  \resumeSubHeadingListEnd
  

%------RELEVANT COURSEWORK-------
\section{COURSEWORK / SKILLS}
    %\resumeSubHeadingListStart
        \begin{multicols}{4}
            \begin{itemize}[itemsep=-2pt, parsep=5pt]
                \item Data Structures \& Algorithms
                \item Operating Systems
                \item Computer Sciences
                \item OOPs Concept
                \item Mobile Application Development
                \item Blockchain
                \item Programming Languages
                \item Database Management System (DBMS)
                \item Web API Application Development
                \item Distributed System
                \item Cryptography
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{WORKING EXPERIENCE}
  \resumeSubHeadingListStart

  \resumeSubheading
      {Beowulf Blockchain\href{https://beowulfchain.com/}{\raisebox{-0.1\height}\faExternalLink}}{} % {06 2022 -- Present} 
      {\underline{Part-time smart contract intern}}{Ho Chi Minh City, Vietnam}
      \resumeItemListStart
        \resumeItem{\normalsize{Research, build, deploy smart contracts to different networks.}}
        \resumeItem{\normalsize{Smart contract interaction with different technologies (Node.js, Solidity).}}
        \resumeItem{\normalsize{Backend developer (Node.js).}}
      \resumeItemListEnd


    \resumeSubheading
      {Full-time freelancer\href{https://phnaharris.github.io/}{\raisebox{-0.1\height}\faExternalLink}}{} % {06 2020 -- 06 2021} 
      {\underline{Mobile Application Developer}}{Vietnam}
      \resumeItemListStart
        \resumeItem{\normalsize{Built Web API using ASP.NET MVC patterns.}}
        \resumeItem{\normalsize{Built mobile cross-platform application using Xamarin.Forms.}}
        \resumeItem{\normalsize{Built automation tool to do some works that the customer needs.}}
        \resumeItem{\normalsize{Support customer to use and maintance the product.}}
      \resumeItemListEnd  

    \resumeSubheading
      {Part-time freelancer\href{https://phnaharris.github.io/}{\raisebox{-0.1\height}\faExternalLink}}{} % {06 2019 -- 06 2020} 
      {\underline{Mobile Application Developer}}{Ho Chi Minh City, Vietnam}
      \resumeItemListStart
        \resumeItem{\normalsize{Built mobile cross-platform application using Xamarin.Forms.}}
        \resumeItem{\normalsize{Communicated with the customer and team leader to deeply understand the needs of users and build an application that serves those needs.}}
        \resumeItem{\normalsize{Studied a variety of ASP.NET technical stack as ASP.NET MVC, Selenium, WPF...}}

      \resumeItemListEnd  

  \resumeSubHeadingListEnd
\vspace{-12pt}


%-----------SOFT SKILLS-----------
\section{SOFT SKILLS}
 \begin{itemize}[leftmargin=0.33in, parsep=-2pt]
    \item Passionate about learning new skills for life and technology.
    \item Increase productivity by automating repetitive tasks.
    \item Good at adaptability and problem solving with new
    environment.
    \item Communication skill.
 \end{itemize}
 \vspace{-15pt}


%-----------PROGRAMMING SKILLS-----------
 \section{TECHNICAL SKILLS}
 \begin{itemize}[leftmargin=0.15in, label={}]
     \small{\item{
             \textbf{\normalsize{Languages:}}{ \normalsize{JavaScript (Node.js),
             C\#, C/C++, XAML, T-SQL, Python, Shell, HTML, Arduino, Java, Rust,
             Golang, Solidity...}} \\ 
             \textbf{\normalsize{Developer Tools:}}{ \normalsize{VS Code/Neovim,
             Visual Studio, SQL Server Management Studio, Remix, Android Studio,
             Jupyter Notebook, Postman, ngrok.io...}} \\
             \textbf{\normalsize{Technologies/Frameworks:}}{\normalsize{
                 Express.js, Rocket (Rust), Xamarin.Forms with MVVM pattern,
                 ASP.NET MVC with Entity Framework, WPF, Selenium, Linux, Git,
                 Flutter, Distributed System/Consensus...}} \\ 
         }}
 \end{itemize}
 \vspace{-15pt}


% -----------INVOLVEMENT---------------
\section{EXTRACURRICULAR}
    \resumeSubHeadingListStart
        \resumeSubheading{Google IO Extended Vietnam 2019 \href{https://drive.google.com/drive/folders/1k5h6xw7oFICgEAcnXmVP1wcZdPf8Fa5k?usp=sharing}{\raisebox{-0.1\height}\faExternalLink } }{07 2019}
        {}{Ho Chi Minh City, Vietnam}
            \resumeItemListStart
                \resumeItem{\normalsize{Certificate of Completion present for successfully completing the TensorFlow, Keras and deep learning, without a PhD.}}
                \resumeItem{\normalsize{Certificate of Completion present for successfully completing the Building Beautiful UIs with Flutter.}}
            \resumeItemListEnd

        \resumeSubheading{HCMUS's BLIT Program}{2018}
        {}{Ho Chi Minh City, Vietnam}
            \resumeItemListStart
                \resumeItem{\normalsize{Candidate of 4th round of BLIT Competition at VNUHCM - University of Science.}}
            \resumeItemListEnd
    \resumeSubHeadingListEnd
 \vspace{-11pt}
 
 %-----------CERTIFICATIONS---------------
\section{CERTIFICATIONS}

\hspace{0.15in} $\sbullet[.7] \hspace{0.1cm}$ {\href{https://www.hackerrank.com/certificates/229a5a0f646d}{C\# (Basic) - HackerRank} \href{https://www.hackerrank.com/certificates/229a5a0f646d}{\raisebox{-0.1\height}\faExternalLink }} \hspace{1.3cm}
$\sbullet[.7] \hspace{0.1cm}$ {\href{https://www.linkedin.com/in/phna-harris/details/skills/}{LinkedIn Skill Assessment: C\#, .NET, C/C++, T-SQL,...} \href{https://www.linkedin.com/in/phna-harris/details/skills/}{\raisebox{-0.1\height}\faExternalLink }}

\hspace{0.15in} $\sbullet[.7] \hspace{0.1cm}$ {\href{https://www.hackerrank.com/certificates/7cd765401419}{C (Intermediate) - HackerRank} \href{https://www.hackerrank.com/certificates/7cd765401419}{\raisebox{-0.1\height}\faExternalLink }} \hspace{0.37cm}

\hspace{0.15in} $\sbullet[.7] \hspace{0.1cm}$ {\href{https://www.hackerrank.com/certificates/045cfefad6e1}{SQL (Basic) - HackerRank} \href{https://www.hackerrank.com/certificates/045cfefad6e1}{\raisebox{-0.1\height}\faExternalLink }} \hspace{1.14cm}


%-----------PROJECTS-----------
\section{PROJECTS}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
      {\textbf{\large{IHI}} $|$ \large{Mobile Developer}}{2021}
        \resumeItemListStart
          \resumeItem{\normalsize{The app provides online teaching service for student with
          variety of subjects. With this app, student can purchase courses
          from our partners, study online and review their knowledge with
          our exercise. By using IHI, student can study from everywhere
          they want and with their speed at specific lesson, easily check
          their understanding just with a device which have Internet connection.}}

          \resumeItem{\normalsize{Tech stack: Xamarin.Forms with MVVM pattern, HttpRequest, payment process
          with Momo, ASP.NET MVC Web API with Entity Framework.}}

          %\resumeItem{\textcolor{accent} {\href{https://github.com/phnaphnt/-HCMUS-KTLT-Pong-Game} {\normalsize{Github.}}}}
        \resumeItemListEnd 
        \vspace{-13pt}
   
      \resumeProjectHeading
      {\textbf{\large{Automatic streaming tool}} $|$ \large{Developer}}{2021}
        \resumeItemListStart
          \resumeItem{\normalsize{The automatic tool that allow user to create, edit,
          remove video stream on Youtube. User can create
          Chrome profile associated with Google account,
          choose video you want to stream on Youtube, setup start
          time and end time of that live stream. When the tool
          streaming, user can see quality of that video stream (by
          bitrate, FPS, speed) and buy amount of viewers by third
          party service. User can stream on more than one Google
          account at a time.}}

          \resumeItem{\normalsize{Tech stack: WPF, Selenium with Chrome profile
          interaction, multithreading architecture, Youtube
          streaming with FFMPEG, WinAPI (Process).}}

          %\resumeItem{\textcolor{accent} {\href{https://github.com/phnaphnt/-HCMUS-KTLT-Pong-Game} {\normalsize{Github.}}}}
        \resumeItemListEnd 
        \vspace{-13pt}


      \resumeProjectHeading
      {\textbf{\large{Gamvip account checking tool}} $|$ \large{Developer}}{2021}
        \resumeItemListStart
          \resumeItem{\normalsize{The automatic tool that allow user to load a list of gamvip (a list
          of webgame) account, log in and request account information
          like name, user id, financial information.... User can use
          multithreading architecture to improve tool performance.}}
          
          \resumeItem{\normalsize{Tech stack: WPF, HttpRequest, multithreading architecture.}}
          
          %\resumeItem{\textcolor{accent} {\href{https://github.com/phnaphnt/-HCMUS-KTLT-Pong-Game} {\normalsize{Github.}}}}
        \resumeItemListEnd 
        \vspace{-13pt}
      
      \resumeProjectHeading
      {\textbf{\large{Yahoo account checking tool}} $|$ \large{Developer}}{2020}
        \resumeItemListStart
          \resumeItem{\normalsize{The automatic tool that allow user to load a list of outlook
          email (hotmail and password), check if that email have
          yahoo account linked, save the yahoo account and use
          that account to get account uid and reset a
          corresponding facebook account password. User can
          use multithreading architecture to improve tool
          performance.}}
          
          \resumeItem{\normalsize{Tech stack: WPF, Selenium, multithreading architecture,
          regular expression, mail service library, bypass captcha
          service library, HttpRequest.}}
          
          %\resumeItem{\textcolor{accent} {\href{https://github.com/phnaphnt/-HCMUS-KTLT-Pong-Game} {\normalsize{Github.}}}}
        \resumeItemListEnd 
        \vspace{-13pt}

      \resumeProjectHeading
      {\textbf{\large{Order filtering tool}} $|$ \large{Developer}}{2020}
        \resumeItemListStart
          \resumeItem{\normalsize{The automatic tool that getting all of orders confirmation
          email (email \& password provided), checking and
          filtering details such as color, size, customer information
          (phone, address, email, ...), ... add that details into excel
          files.}}

          \resumeItem{\normalsize{Tech stack: WPF, Selenium, multithreading architecture,
          regular expression, mail service library.}}

          %5\resumeItem{\textcolor{accent} {\href{https://github.com/phnaphnt/-HCMUS-KTLT-Pong-Game} {\normalsize{Github.}}}}
        \resumeItemListEnd 
        \vspace{-13pt}
     
      \resumeProjectHeading
      {\textbf{\large{Spotify password changing tool}} $|$ \large{Developer}}{2020}
        \resumeItemListStart
          \resumeItem{\normalsize{The automatic tool that allow user to load a list of Spotify
          account with its changing password link. The tool follow the link
          automatically, enter password and new password, bypass
          captcha and submit. User can use multithreading architecture
          to improve tool performance.}}

          \resumeItem{\normalsize{Tech stack: WPF, HttpRequest, multithreading architecture,
          Selenium.}}

          %\resumeItem{\textcolor{accent} {\href{https://github.com/phnaphnt/-HCMUS-KTLT-Pong-Game} {\normalsize{Github.}}}}
        \resumeItemListEnd 
        \vspace{-13pt}

      \pagebreak

      \resumeProjectHeading
       {\textbf{\large{Seanato}} $|$ \large{Mobile Developer}}{2019}
          \resumeItemListStart
            \resumeItem{\normalsize{The app provides ferry booking, cable car tickets, tickets
            to amusement parks of Vinpearl and Sun World.
            \\Seanato is the first and only application that provides a
            ticketing service in the field of maritime tourism, linking
            most of the major ferry carriers in the Kien Giang province
            to provide customers with optimal choice and the most
            effective.
            \\Seanato also cooperates with Vietnam's major travel groups such as Vingroup, Sun World.}}
            
            \resumeItem{\normalsize{Tech stack: Xamarin.Forms with MVVM pattern, HttpRequest, payment
            process with Momo \& Alepay...}}
            
            %\resumeItem{\textcolor{accent} {\href{https://github.com/phnaphnt/-HCMUS-KTLT-Pong-Game} {\normalsize{Github.}}}}
          \resumeItemListEnd 
          \vspace{-13pt}
        
      \resumeProjectHeading
        {\textbf{\large{Pong game}} $|$ \large{Teamlead, Developer}}{2019}
          \resumeItemListStart
            \resumeItem{\normalsize{Pong game is my end-of-term project of Programming
            Engineering term at university that use basic skill with C++
            programming language.}}
            
            \resumeItem{\normalsize{Tech stack: C++ programming language.}}
            
            \resumeItem{\textcolor{accent} {\href{https://github.com/phnaphnt/-HCMUS-KTLT-Pong-Game} {\normalsize{Github.}}}}
          \resumeItemListEnd 
          \vspace{-13pt}





      % \resumeProjectHeading
      %     {{\textbf{\large{\underline{Project Name}}}} $|$ \large{Technology Stack Used}}{2021}
      %     \resumeItemListStart
      %       \resumeItem{\normalsize{About project \textbf{highlight key points}.}}
      %       \resumeItem{\textcolor{accent} {\href{Project Link} {\underline{\normalsize{Download}}}}}
      %     \resumeItemListEnd
      %     \vspace{-13pt}
    \resumeSubHeadingListEnd
\vspace{-12pt}

%

\end{document}
